Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-12 paper/paper.tex
Fixing

  Due to the differences in merger histories, the metallicity
  evolution of h258 and h277 also differ at early times.  Figure
  \ref{fig:TwoGalaxies} shows the history of the mean metallicity of
  recently formed stars vs time (thick solid lines), where we define
  recent as within the past 50 Myr.  The shaded regions correspond to
  one standard deviation of the mean, while the thick dashed lines
  represent the top and bottom 90\%.  We see that the early evolution
  of the metal properties of these galaxies does differ - between 0.5
  and 6 Gyr, h277 hosts a \emph{modestly}  more metal-rich population than
  h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
  present-day observables.  However, for binary black holes depend sensitively on all low metallicity star formation
  over cosmic time; as we show below, these small differences can have an observable impact at present.

>>>>

  Due to the differences in merger histories, the star formation histories and metallicity
  evolution of h258 and h277 also differ at early times.  Figure
  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of the two galaxies.  The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.   The right panel shows the mean metallicity of
  recently formed stars vs time (thick solid lines), where we define
  recent as within the past 50 Myr.  The shaded regions correspond to
  one standard deviation of the mean, while the thick dashed lines
  represent the top and bottom 90\%.  We see that the early evolution
  of the metal properties of these galaxies does differ - between 0.5
  and 6 Gyr, h277 hosts a \emph{modestly}  more metal-rich population than
  h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
  present-day observables.  However, for binary black holes depend sensitively on all low metallicity star formation
  over cosmic time; as we show below, these small differences can have an observable impact at present.
